Twisted 11-dimensional supergravity, I

### 2021-08-09 draft.tex
draft

\begin{prop}
The complex \eqref{eq:poissfields} is equipped with the structure of an interacting Poisson BV theory. 
\end{prop}

Heuristically, we can write the action in the following non-local form
\[
\frac{1}{1-\nu} \mu^2 \eta + (\del^{-1} \eta) \eta^2 .
\]

@@

>>>>

\begin{prop}
The complex \eqref{eq:poissfields} is equipped with the structure of an interacting Poisson BV theory.
Let $\cG = \cG(X \times L)$ be the resulting $L_\infty$ algebra...
\end{prop}

Heuristically, we can write the action in the following non-local form
\[
\frac{1}{1-\nu} \mu^2 \eta + (\del^{-1} \eta) \eta^2 .
\]
\brian{are there more terms involving higher forms?}

The first few nonzero brackets are
\begin{align*}
[\mu]_1 & = \dbar \mu + \div \mu \\
[\eta]_1 & = \dbar \eta + \del \eta \\ 
[\mu_1,\mu_2]_2 & = \div (\mu_1 \wedge \mu_2) \\
[\mu, \eta]_2 & = \mu \vee \del \eta \\
[\eta_1,\eta_2]_2 & = \# \Omega^{-1} \vee (\eta_1 \wedge \eta_2)  \\
[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
[\nu, \mu,\eta]_3 & = \nu \mu \del \eta
\end{align*}
\brian{coefficients}
For $k \geq 2$ the general formula for the $k$-ary bracket is 
\begin{align*}
[\eta_1,\eta_2]_2 & = \# \Omega^{-1} \vee (\eta_1 \wedge \eta_2)  \\
[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \# \div(\nu_1 \cdots \nu_{k-2} \mu_1 \wedge \mu_2) \\ 
[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu,\eta]_{k} & = \# \nu_1 \cdots \nu_{k-2} (\mu \vee \del \eta) .
\end{align*}

\parsec[]
Consider the theory on $\CC^3 \times \RR$. 
There is a quasi-isomorphism of $L_\infty$ Lie algebras $\CC \simeq \cG (\CC^3 \times \RR)$.

\parsec[]
Consider the theory on $\CC^5 \times \RR$.

\begin{prop}
There is a quasi-isomorphism of super $L_\infty$ algebras 
\[
E(5,10) \xto{\simeq} \cG(\CC^5 \times \RR) .
\]
This lifts to map of super $L_\infty$ algebras $E(5,10) \to \cL(\CC^5 \times \RR)$ whose kernel is $\CC$.
\end{prop}

@@

\appendix
